\begin{answer}

A) Yes, function K is a valid kermel
\[K(x,z) = K_1(x,z) + K_2(x,z)\]
The problem states that both $K_1$ and $K_2$ are kernels, therefore $K_1$ and $K_2$ must both be symmetric and positive semidefinite.
\[z^T K_1z \geq 0 \]
and
\[ z^TK_2z \geq 0 \]
The sum of two positive semidefinite matrices is also symmetric and positive semidefinite.
As a result, the function K is symmetric and semidefinite, and it is a valid kernel.
\[z^T K_1z \geq 0 + z^T K_2z \geq 0 \] 
\[ z^T (K_1 + K_2)z \geq 0 &=& \] 
\[\[ z^TKz \geq 0 \] 

B) No, K is not a valid kernel
\[K(x,z) = K_1(x,z) - K_2(x,z)\]
Substracting a symmetric matrix from another one, will cause the resulting matrix to be negative semidefinite.
The new function K is not a kernel because it is now negative semidefinite.
\[z^T K_1z \geq 0 - z^T K_2z \geq 0 \] 
\[ z^T (K_1 - K_2)z \leq 0 &=& \] 
\[\[ zKz \leq 0 \] 

C) Yes, K is a valid kernel
\[K(x,z) = aK_1(x,z)\]
Since $K_1$ is symmetric and positive semidefinite, and given that a is a positive real number, the resulting multiplication results in function K being both symmetric and positive semidefinite.
\[z^T K_1z \geq 0 \]
and $a > 0$
\[a * z^T K_1z \geq 0 \]

D) No, K is not a valid kernel
\[ K(x,z) = -aK_1(x,z) \]
$K_1$ is a kernel, and a is a positive real number; however, the negative turns K into a negative semidefinite matrix function.
\[ ((-1) * (a>0) * (z^T Kz \geq 0) =\]
\[ ((-1) * (a*z^T Kz \geq 0) =\]
\[ -a*z^T Kz \leq 0 \]

E) Yes. K is a valid kernel
\[K(x,z) = K_1(x,z)K_2(x,z)\]
Each $K_1$ and $K_2$ are both kernels that are symmetric and positive semidefinite.\\
\[K_1(x,z) = \phi(x)^T \phi(z) \]
\[K_1(x,z) = \sum\phi(x_i)\phi(z_i)\]
\[K_2(x,z) = \phi(x)^T \phi(z) \]
\[K_2(x,z) = \sum\phi(x_j)\phi(z_j)\]
Therefore,
\[K(x,z) = K_1(x,z)K_2(x,z)\]
\[K(x,z) = \sum\phi(x_i)\phi(z_i)\sum\phi(x_j)\phi(z_j)\] 
\[ = \sum\sum \phi(x_i)\phi(z_i)\phi(x_j)\phi(z_j)\]
\[ = \sum\sum \phi(x_i)\phi(x_j)\phi(z_i)\phi(z_j)\]
Since $X_ij = x_ix_j$,
\[ = \sum \phi_i_j(x_i) \phi_i_j(z_i) \]
\[K(x,z) = \phi_i_j(x_i)^T \phi_i_j(z_i) \]
The final function K is the form of the kernel function
\[K(x,z) = \langle\phi(x), \phi(z)\rangle \]

F) Yes, K is a valid kernel
\[K(x,z) = f(x)f(z) \]
We have that f is a real-valued function, f: $R^n \rightarrow R$.
Since the f(x) function is a scalar, f(x) x f(z) is equal to $f(x)^Tf(z)$
\[K(x,z) = f(x)^T f(z) \]
The function f(X) takes the value of the kernel function, where:
\[K(x,z) = \langle\phi(x), \phi(z)\rangle \]

G) Yes, K is a valid kernel
\[K(x,z) = K_3(\phi(x),\phi(z)) \]
Since $K_3$ is a kernel, $R^d x R^d$, the functions $\phi(x)$ and $\phi(z)$ are also positive semidefinite.
\[\[ z^T K_3z \geq 0 \] 


H) Yes, K is a valid kernel
\[K(x,z) = p(K_1(x,z))\]
\[b_1 K_3 (x,z) + . . . + b_{i-1} K_3(x,z)^{i-1} + b_i K_3 (x,z)^i \]
The polynomial function can be proved by knowing that: 

1) The sum of two kernels is also a kernel

2) The multiplication of a kernel and another positive number is also a kernel. (p(x) is a polynomial over x with positive coefficients.) 

3) The power of a kernel is also a kernel
Therefore The polynomial of a kernel is also a kernel
\[\[ z^T K_3z \geq 0 \] 


\end{answer}
